\textcolor{red}{Simple} connectome inference using partial correlation from imaging calcium signal

### 2014-06-17 article.tex
capitalize figure
use appropriate figure
rewrote section on the hard treshold signal

\begin{figure}[bth]
\includegraphics[width=\linewidth]{images/fig_filtering_recut.png}
\caption{Filtering steps. \textcolor{red}{TODO remake in pdf}}
\label{fig:fitlering}
\end{figure}

The raw signal (original signal of Figure \ref{fig:fitlering}) is very noisy
due to light scattering artifacts that ordinarily affects the quality of the
recording (\cite{lichtman2011big}). A low-pass filter is first applied to
filter high frequency noises with one of the following filter designs
\begin{align}
% symmetrical median filter
x^t_i &\leftarrow x^{t-1}_i + x^{t}_i + x^{t+1}_i \label{eq:symetric-median}, \\
% asymmetrical weighted median
x^t_i &\leftarrow 0.4 x^{t-3}_i + 0.6 x^{t-2}_i + 0.8 x^{t-1}_i + x_{t}^i.
\label{eq:weighted-asymetric-median}.
\end{align}

A neuron spike lasts on average $1ms$ to $2ms$, while current optical
device have a time resolution of $20ms$. Considering the short delay for a
communication between neurons and slow decay of fluorescence signal, we
can filter low frequencies through an asymmetrical discrete derivative filter
\begin{align}
x^{t,d}_{i} \leftarrow x^{t}_i - x_{t-1}^i.
\end{align}
When slow signals variations are filtered (H-P signals of figure
\ref{fig:filtering}), only remains spike positions.
\textcolor{red}{Pourquoi sur la figure, on a pas de signal avec une dérivée
                négative?}

By nature, the firing event is really fast and in order to
retrieve the connectivity from them, it is necessary to link a burst to a
couple of timesteps (ideally one). The small decay for the fluorescent calcium indicator implies a signal
variation during a long time interval. Firing event are represented by strong
variations in the neuron activity. Therefore we apply a hard-tresholding
filter $x^{t,d}_i = x^{t,d}_i \mathbb{1}(x^{t,d}_i \geq \tau)$ where the
threshold $\tau$ should be taken positive and non-close to zero to
respectivelty only keep rising edges and strong variations.

As a result, we get a binary-like signal with the true activity when a burst
happens and with a true zero when the neuron is inactive.

>>>>

\begin{figure}[bth]
\includegraphics[width=\linewidth]{images/fig_filtering}
\caption{Filtering steps. \textcolor{red}{TODO remake in pdf}}
\label{fig:filtered-signal}
\end{figure}

The raw signal (original signal of Figure \ref{fig:filtered-signal}) is very noisy
due to light scattering artifacts that ordinarily affects the quality of the
recording (\cite{lichtman2011big}). A low-pass filter is first applied to
filter high frequency noises with one of the following filter designs
\begin{align}
% symmetrical median filter
x^t_i &\leftarrow x^{t-1}_i + x^{t}_i + x^{t+1}_i \label{eq:symetric-median}, \\
% asymmetrical weighted median
x^t_i &\leftarrow 0.4 x^{t-3}_i + 0.6 x^{t-2}_i + 0.8 x^{t-1}_i + x_{t}^i.
\label{eq:weighted-asymetric-median}.
\end{align}

A neuron spike lasts on average $1ms$ to $2ms$, while current optical
device have a time resolution of $20ms$. Considering the short delay for a
communication between neurons and slow decay of fluorescence signal, we
filter low frequencies through a high pass filter
\begin{align}
% an asymmetrical discrete derivative filter
x^{t,d}_{i} &\leftarrow x^{t}_i - x_{t-1}^i. \label{eq:high-pass-filter}
\end{align}

Whenever the low and high pass filtered have been applied, the remaining signal
(H-P signal of Figure \ref{fig:filtered-signal}) is the discrete
derivative of the fluorescence calcium concentration. To further filter out
small signal variations which are due to noise, we apply a hard-threshold
filter
\begin{align}
x^{t,d}_i &\leftarrow x^{t,d}_i \mathbb{1}(x^{t,d}_i \geq \tau) \text{ with } \tau > 0.
\end{align}
